---
title: "Pre-compute Figures"
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
# ── Run this file ONCE to build all heavy figures ──────────────────────────
# Figures are saved to figures/precomputed/ and reused by 30-results.qmd.
# Set FORCE_REBUILD <- TRUE to regenerate even if the PNG already exists.
FORCE_REBUILD <- FALSE

dir.create("figures/precomputed", showWarnings = FALSE, recursive = TRUE)

needs_build <- function(path) FORCE_REBUILD || !file.exists(path)
```

```{r packages}
library(magick)
library(tidyverse)
library(ggplot2)
library(cowplot)
```

```{r helpers}
# ── Image-composite helpers (same as 30-results.qmd) ──────────────────────

COL_BLUE <- "#4472C4"
COL_GREY <- "#A6A6A6"
PAL_COMP <- c(Soma = "#4A90D9", Axon = "#E07B54")

theme_wb <- function() {
  theme_classic(base_size = 13) +
    theme(
      axis.text.x        = element_text(angle = 35, hjust = 1, size = 11),
      plot.title         = element_text(face = "bold", size = 13),
      plot.subtitle      = element_text(size = 10, color = "grey45"),
      panel.grid.major.y = element_line(color = "grey90"),
      legend.position    = "none"
    )
}

PANEL_W  <- 500L; LEFT_W <- 90L; RIGHT_W <- 80L
TOTAL_W  <- LEFT_W + PANEL_W + RIGHT_W
HEADER_H <- 38L;  GAP_H  <- 10L; FS <- 15L; BG <- "white"

fit_w <- function(img) {
  h <- as.integer(round(image_info(img)$height * PANEL_W / image_info(img)$width))
  image_resize(img, paste0(PANEL_W, "x", h, "!"))
}
add_border <- function(img, px = 2L) image_border(img, "black", paste0(px, "x", px))

make_wb_row <- function(img, kda_label, protein_label) {
  h     <- image_info(img)$height
  left  <- image_blank(LEFT_W,  h, color = BG) |>
    image_annotate(kda_label,     size = FS-1, color="black", font="sans",
                   gravity="West",  location="+4+0")
  right <- image_blank(RIGHT_W, h, color = BG) |>
    image_annotate(protein_label, size = FS,   color="black", font="sans",
                   style="italic", gravity="West", location="+6+0")
  image_append(c(left, img, right), stack = FALSE)
}

make_header <- function(labels) {
  header <- image_blank(TOTAL_W, HEADER_H, color = BG)
  col_w  <- as.integer(PANEL_W / length(labels))
  for (i in seq_along(labels)) {
    x <- LEFT_W + as.integer((i-1L)*col_w + col_w/2L) - 28L
    header <- image_annotate(header, labels[i], size=FS-2, color="black",
                              font="sans", weight=700, gravity="NorthWest",
                              location=paste0("+", x, "+2"))
  }
  header
}

build_composite <- function(tau_img, act_img, tau_kda, act_kda,
                             tau_label, act_label, lane_labels, title_label) {
  tau_img   <- fit_w(tau_img) |> add_border()
  act_img   <- fit_w(act_img) |> add_border()
  gap       <- image_blank(TOTAL_W, GAP_H, color = BG)
  title_row <- image_blank(TOTAL_W, 70L, color = BG) |>
    image_annotate(title_label, size=FS+22, color="black", font="sans",
                   weight=700, gravity="North",
                   location="+0+6")
  image_append(
    c(title_row, make_header(lane_labels),
      make_wb_row(tau_img, tau_kda, tau_label), gap,
      make_wb_row(act_img, act_kda, act_label)),
    stack = TRUE
  ) |> image_border(BG, "8x8")
}

make_if_grid <- function(paths, labels) {
  imgs <- lapply(seq_along(paths), function(i) {
    img <- image_read(paths[[i]])
    img <- image_scale(img, "2400x2400")
    image_annotate(img, labels[[i]], gravity="SouthWest", location="+8+6",
                   size=40, color="white", font="Arial-Bold", boxcolor="transparent")
  })
  row1 <- image_append(c(imgs[[1]], imgs[[2]]))
  row2 <- image_append(c(imgs[[3]], imgs[[4]]))
  image_append(c(row1, row2), stack = TRUE)
}

save_fig <- function(path, p, width = 14, height = 14, dpi = 150) {
  ggsave(path, plot = p, width = width, height = height,
         dpi = dpi, units = "in", bg = "white")
  message("Saved: ", path)
}
```

---

## Tuj1 (Gr) / Tau (Rd) — Channel-swap test (MF_090825)

```{r build-tuj1-tau-swapped}
out <- "figures/precomputed/fig-tuj1-tau-swapped.png"

if (needs_build(out)) {
  CHDIR <- "./ZeissImages/channels_MF_090825_20260309_134939"

  # 6 loose TIF files in root: Ctrl, ProNGF, BDNF × AF488 + AF568
  treatments <- list(
    list(label  = "Ctrl",
         f488   = "Ctrl-Tuj1_488-Tau_555_2_DAPI+AF488.tif",
         f568   = "Ctrl-Tuj1_488-Tau_555_2_DAPI+AF568.tif"),
    list(label  = "ProNGF",
         f488   = "ProNGF_in_Axons_Tuj1_488_Tau_555_1_DAPI+AF488.tif",
         f568   = "ProNGF_in_Axons_Tuj1_488_Tau_555_1_DAPI+AF568.tif"),
    list(label  = "BDNF",
         f488   = "BDNF_in_Axons_Tuj1_488_Tau_555_1_DAPI+AF488.tif",
         f568   = "BDNF_in_Axons_Tuj1_488_Tau_555_1_DAPI+AF568.tif")
  )

  IMG_W    <- 1000L
  GAP_W    <-   25L
  LABEL_W  <-  180L
  HEADER_H <-   60L
  FONT_SZ  <-   48L

  make_row <- function(t) {
    img_tuj1 <- image_read(file.path(CHDIR, t$f488)) |>
      image_scale(paste0(IMG_W, "x")) |> image_border("white", "3x3")
    img_tau  <- image_read(file.path(CHDIR, t$f568)) |>
      image_scale(paste0(IMG_W, "x")) |> image_border("white", "3x3")

    h   <- image_info(img_tuj1)$height
    gap <- image_blank(GAP_W,   h, color = "white")
    lbl <- image_blank(LABEL_W, h, color = "white") |>
      image_annotate(t$label, gravity = "West", location = "+12+0",
                     size = FONT_SZ, color = "black", font = "Arial-Bold")
    image_append(c(img_tuj1, gap, img_tau, gap, lbl))
  }

  rows    <- lapply(treatments, make_row)
  row_w   <- image_info(rows[[1]])$width
  row_gap <- image_blank(row_w, GAP_W, color = "white")

  # Column headers
  panel_w_actual <- image_info(
    image_read(file.path(CHDIR, treatments[[1]]$f488)) |>
    image_scale(paste0(IMG_W, "x"))
  )$width + 6L

  x1 <- as.integer(panel_w_actual / 2L) - 100L
  x2 <- as.integer(panel_w_actual + GAP_W + panel_w_actual / 2L) - 90L

  header <- image_blank(row_w, HEADER_H, color = "white") |>
    image_annotate("DAPI + Tuj1 (Gr)", gravity = "NorthWest",
                   location = paste0("+", x1, "+14"),
                   size = FONT_SZ, color = "black", font = "Arial-Bold") |>
    image_annotate("DAPI + Tau (Rd)", gravity = "NorthWest",
                   location = paste0("+", x2, "+14"),
                   size = FONT_SZ, color = "black", font = "Arial-Bold")

  combined <- image_append(
    c(header, rows[[1]], row_gap, rows[[2]], row_gap, rows[[3]]),
    stack = TRUE
  )

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## p75 / Tuj1 / Tau — Ctrl vs ProNGF (MF_072525)

```{r build-p75-tuj1-tau}
out <- "figures/precomputed/fig-p75-tuj1-tau.png"

if (needs_build(out)) {
  CHDIR <- "./ZeissImages/channels_MF_072525_20260318_042930"

  treatments <- list(
    list(label = "Ctrl",   folder = "Ctrl_Axons_p75_488_Tuj1_555__Tau_633_n1"),
    list(label = "ProNGF", folder = "ProNGF_Axons_p75_488_Tuj1_555__Tau_633_n1")
  )

  # AF488 = p75, AF568 = Tuj1, AF633 = Tau
  channels <- list(
    list(suffix = "_DAPI+AF488.tif", header = "DAPI + p75 (Gr)"),
    list(suffix = "_DAPI+AF568.tif", header = "DAPI + Tuj1 (Rd)"),
    list(suffix = "_DAPI+AF633.tif", header = "DAPI + Tau (FR)")
  )

  IMG_W    <- 900L
  GAP_W    <-  25L
  LABEL_W  <- 180L
  HEADER_H <-  60L
  FONT_SZ  <-  32L

  make_row <- function(t) {
    fdir <- file.path(CHDIR, t$folder)
    imgs <- lapply(channels, function(ch) {
      image_read(file.path(fdir, paste0(t$folder, ch$suffix))) |>
        image_scale(paste0(IMG_W, "x")) |>
        image_border("white", "3x3")
    })

    h   <- image_info(imgs[[1]])$height
    gap <- image_blank(GAP_W,   h, color = "white")
    lbl <- image_blank(LABEL_W, h, color = "white") |>
      image_annotate(t$label, gravity = "West", location = "+12+0",
                     size = FONT_SZ, color = "black", font = "Arial-Bold")

    image_append(c(imgs[[1]], gap, imgs[[2]], gap, imgs[[3]], gap, lbl))
  }

  rows    <- lapply(treatments, make_row)
  row_w   <- image_info(rows[[1]])$width
  row_h   <- image_info(rows[[1]])$height
  row_gap <- image_blank(row_w, GAP_W, color = "white")

  # Column headers centred over each panel
  panel_w_actual <- image_info(
    image_read(file.path(CHDIR, treatments[[1]]$folder,
               paste0(treatments[[1]]$folder, "_DAPI+AF488.tif"))) |>
    image_scale(paste0(IMG_W, "x"))
  )$width + 6L  # +6 for border

  header <- image_blank(row_w, HEADER_H, color = "white")
  for (i in seq_along(channels)) {
    x <- as.integer((i - 1L) * (panel_w_actual + GAP_W) + panel_w_actual / 2L) - 80L
    header <- image_annotate(header, channels[[i]]$header,
                             gravity = "NorthWest",
                             location = paste0("+", x, "+14"),
                             size = FONT_SZ, color = "black", font = "Arial-Bold")
  }

  combined <- image_append(
    c(header, rows[[1]], row_gap, rows[[2]]),
    stack = TRUE
  )

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## TrkB / Tau IF Grid (MF_070825)

```{r build-trkb-tau}
out <- "figures/precomputed/fig-trkb-tau.png"

if (needs_build(out)) {
  CHDIR <- "./ZeissImages/channels_MF_070825_20260317_130135"

  treatments <- list(
    list(label = "Ctrl",          folder = "Ctrl_Axons_TrkB_488_TAU_555_n1"),
    list(label = "ProNGF",        folder = "ProNGF_Axons_TrkB_488_TAU_555_"),
    list(label = "BDNF",          folder = "BDNF_Axons_TrkB_488_TAU_555_n1"),
    list(label = "ProNGF + BDNF", folder = "ProNGF_and_BDNF_Axons_TrkB_488_TAU_555_n1")
  )

  IMG_W   <- 1200L   # width each panel is scaled to
  GAP_W   <-   20L   # pixel gap between panels and rows
  LABEL_W <-  200L   # width of treatment label column on right
  HEADER_H <-  60L   # height of column-header row
  FONT_SZ  <-  54L

  # Build one row per treatment: [AF488 | gap | AF568 | gap | label]
  make_row <- function(t) {
    fdir <- file.path(CHDIR, t$folder)
    img_trkb <- image_read(file.path(fdir, paste0(t$folder, "_DAPI+AF488.tif"))) |>
      image_scale(paste0(IMG_W, "x"))
    img_tau  <- image_read(file.path(fdir, paste0(t$folder, "_DAPI+AF568.tif"))) |>
      image_scale(paste0(IMG_W, "x"))

    h    <- image_info(img_trkb)$height
    gap  <- image_blank(GAP_W,   h, color = "white")
    lbl  <- image_blank(LABEL_W, h, color = "white") |>
      image_annotate(t$label, gravity = "West", location = "+12+0",
                     size = FONT_SZ, color = "black", font = "Arial-Bold")
    image_append(c(img_trkb, gap, img_tau, gap, lbl))
  }

  rows <- lapply(treatments, make_row)

  row_w <- image_info(rows[[1]])$width
  row_h <- image_info(rows[[1]])$height

  # Column header row
  header <- image_blank(row_w, HEADER_H, color = "white")
  # Center each label over its column
  x_trkb <- as.integer(IMG_W / 2) - 120L
  x_tau  <- IMG_W + GAP_W + as.integer(IMG_W / 2) - 100L
  header <- header |>
    image_annotate("DAPI + TrkB (Gr)", gravity = "NorthWest",
                   location = paste0("+", x_trkb, "+12"),
                   size = FONT_SZ, color = "black", font = "Arial-Bold") |>
    image_annotate("DAPI + Tau (Rd)", gravity = "NorthWest",
                   location = paste0("+", x_tau, "+12"),
                   size = FONT_SZ, color = "black", font = "Arial-Bold")

  row_gap <- image_blank(row_w, GAP_W, color = "white")

  combined <- image_append(
    c(header,
      rows[[1]], row_gap,
      rows[[2]], row_gap,
      rows[[3]], row_gap,
      rows[[4]]),
    stack = TRUE
  )

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Tau Distribution Crops

```{r build-tau-distribution}
out <- "figures/precomputed/fig-tau-distribution.png"

if (needs_build(out)) {
  CHDIR <- "./ZeissImages/channels_MF_070825_20260317_130135"

  crops <- list(
    list(label = "Ctrl",   file = "Ctrl_Axons_TrkB_488_TAU_555_n2_AF568-1_crop.tif"),
    list(label = "ProNGF", file = "ProNGF_Axons_TrkB_488_TAU_555_n2_AF568-1_crop.tif"),
    list(label = "BDNF",   file = "BDNF_Axons_TrkB_488_TAU_555_n1_AF568-1_crop.tif")
  )

  IMG_W   <- 1800L
  GAP_H   <-   30L
  LABEL_W <-  180L
  FONT_SZ <-   57L

  # Each row: image on left, treatment label on right
  make_row <- function(cr) {
    img <- image_read(file.path(CHDIR, cr$file)) |>
      image_scale(paste0(IMG_W, "x")) |>
      image_border("white", "3x3")
    h   <- image_info(img)$height
    lbl <- image_blank(LABEL_W, h, color = "white") |>
      image_annotate(cr$label, gravity = "West", location = "+12+0",
                     size = FONT_SZ, color = "black", font = "Arial-Bold")
    image_append(c(img, lbl))
  }

  rows  <- lapply(crops, make_row)
  row_w <- image_info(rows[[1]])$width
  gap   <- image_blank(row_w, GAP_H, color = "white")

  combined <- image_append(
    c(rows[[1]], gap, rows[[2]], gap, rows[[3]]),
    stack = TRUE
  )

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## IF Figures — p75 / Tau / Tuj1 (Ctrl, BDNF, proNGF)

```{r build-if-combined}
out <- "figures/precomputed/fig-if-combined.png"

if (needs_build(out)) {
  CHDIR <- "./ZeissImages/channels_101625-MF_20260309_114651"

  # All 6 TIF files sit directly in CHDIR (root level, not in subfolders)
  # Channels: AF488 = p75 (Gr), AF568 = Tau (Rd), dodec = Tuj1 (FR)
  conditions <- list(
    list(label = "Ctrl",
         p75   = "Ctrl_p75_488_Tau_555_Tuj1_594_grooves_2_long_axons_DAPI+AF488.tif",
         tau   = "Ctrl_p75_488_Tau_555_Tuj1_594_grooves_2_long_axons_DAPI+AF568.tif",
         tuj1  = "Ctrl_p75_488_Tau_555_Tuj1_594_grooves_2_long_axons_DAPI+dodec.tif"),
    list(label = "proNGF",
         p75   = "proNGF_p75_488_Tau_555_Tuj1_594_grooves_very_good_DAPI+AF488.tif",
         tau   = "proNGF_p75_488_Tau_555_Tuj1_594_grooves_very_good_DAPI+AF568.tif",
         tuj1  = "proNGF_p75_488_Tau_555_Tuj1_594_grooves_very_good_DAPI+dodec.tif"),
    list(label = "BDNF",
         p75   = "BDNF_p75_488_Tau_555_Tuj1_594_grooves_2_DAPI+AF488.tif",
         tau   = "BDNF_p75_488_Tau_555_Tuj1_594_grooves_2_DAPI+AF568.tif",
         tuj1  = "BDNF_p75_488_Tau_555_Tuj1_594_grooves_2_DAPI+dodec.tif")
  )

  IMG_W    <- 900L
  GAP_W    <-  25L
  LABEL_W  <- 180L
  HEADER_H <-  60L
  FONT_SZ  <-  32L

  make_row <- function(cond) {
    img_p75  <- image_read(file.path(CHDIR, cond$p75))  |>
      image_scale(paste0(IMG_W, "x")) |> image_border("white", "3x3")
    img_tau  <- image_read(file.path(CHDIR, cond$tau))  |>
      image_scale(paste0(IMG_W, "x")) |> image_border("white", "3x3")
    img_tuj1 <- image_read(file.path(CHDIR, cond$tuj1)) |>
      image_scale(paste0(IMG_W, "x")) |> image_border("white", "3x3")

    h   <- image_info(img_p75)$height
    gap <- image_blank(GAP_W,   h, color = "white")
    lbl <- image_blank(LABEL_W, h, color = "white") |>
      image_annotate(cond$label, gravity = "West", location = "+12+0",
                     size = FONT_SZ, color = "black", font = "Arial-Bold")
    image_append(c(img_p75, gap, img_tau, gap, img_tuj1, gap, lbl))
  }

  rows    <- lapply(conditions, make_row)
  row_w   <- image_info(rows[[1]])$width
  row_gap <- image_blank(row_w, GAP_W, color = "white")

  # Column headers centred over each panel
  panel_w_actual <- image_info(
    image_read(file.path(CHDIR, conditions[[1]]$p75)) |>
    image_scale(paste0(IMG_W, "x"))
  )$width + 6L   # +6 for border

  col_headers <- c("DAPI + p75 (Gr)", "DAPI + Tau (Rd)", "DAPI + Tuj1 (FR)")
  header <- image_blank(row_w, HEADER_H, color = "white")
  for (i in seq_along(col_headers)) {
    x <- as.integer((i - 1L) * (panel_w_actual + GAP_W) + panel_w_actual / 2L) - 95L
    header <- image_annotate(header, col_headers[i], gravity = "NorthWest",
                             location = paste0("+", x, "+14"),
                             size = FONT_SZ, color = "black", font = "Arial-Bold")
  }

  combined <- image_append(
    c(header, rows[[1]], row_gap, rows[[2]], row_gap, rows[[3]]),
    stack = TRUE
  )

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Western Blot — July 2025 (proNGF / BDNF)

```{r build-jul25-combined}
out <- "figures/precomputed/fig-jul25-combined.png"

if (needs_build(out)) {
  # ── Blot composite ────────────────────────────────────────────────────────
  lane_labels_jul <- c("Soma\nCtrl", "Soma\nProNGF", "Soma\nBDNF", "Soma\npN+B",
                       "Axon\nCtrl", "Axon\nProNGF", "Axon\nBDNF", "Axon\npN+B")
  jul_comp <- build_composite(
    tau_img     = image_read("ImagesTif/ELINA 2025-07-08 10h15m12s_DyLight_800_TauActinPB-invert_crop_tau.tif"),
    act_img     = image_read("ImagesTif/ELINA 2025-07-08 10h15m12s_DyLight_800_TauActinPB-1_crop_inverted_actin.tif"),
    tau_kda="56 kDa", act_kda="42 kDa", tau_label="Tau", act_label="Actin",
    lane_labels=lane_labels_jul, title_label="Soma + Axon"
  )

  # ── Quantification data ───────────────────────────────────────────────────
  cond_lvls_jul <- c("Ctrl", "ProNGF", "BDNF", "ProNGF +BDNF")
  raw_jul <- read_csv("ImagesCSV/July25_IRDye_800_Ms_Tau_Actin_quantification.csv",
                      show_col_types=FALSE) |>
    rename(row_id=1, area=Area) |>
    mutate(band=rep(1:2, times=8), lane=rep(1:8, each=2))
  band_map_jul <- read_csv("ImagesCSV/BandMapping_ExperimentJuly25.csv",  show_col_types=FALSE)
  lane_map_jul <- read_csv("ImagesCSV/LaneMapping_ExperimentJuly25.csv",  show_col_types=FALSE)

  df_jul <- raw_jul |>
    left_join(band_map_jul, by=c("band"="Band")) |>
    left_join(lane_map_jul, by=c("lane"="Lane")) |>
    select(lane, Condition, Compartment, Protein, area) |>
    pivot_wider(names_from=Protein, values_from=area) |>
    mutate(Tau_Actin   = Tau / Actin,
           Condition   = factor(Condition,   levels=cond_lvls_jul),
           Compartment = factor(Compartment, levels=c("Soma","Axon")))

  # ── Panels: A = blot image, B = Tau/Actin ratio ─────────────────────────
  pA <- ggdraw() + draw_image(jul_comp)
  pB <- ggplot(df_jul, aes(Condition, Tau_Actin, fill=Compartment)) +
    geom_col(position=position_dodge(width=0.65), width=0.6, color="white") +
    scale_fill_manual(values=PAL_COMP) +
    scale_y_continuous(expand=expansion(mult=c(0,0.12))) +
    labs(x=NULL, y="Tau / Actin (a.u.)", fill="Compartment") +
    theme_wb() + theme(legend.position="right")

  fig <- plot_grid(pA, pB, ncol=2,
                   labels=c("A","B"), label_size=18, label_fontface="bold",
                   rel_widths=c(1.2, 1))
  save_fig(out, fig, width=14, height=7)
} else { message("Cached: ", out) }
```

---

## Western Blot — September 2025 (Time Course)

```{r build-sep-combined}
out <- "figures/precomputed/fig-sep-combined.png"

if (needs_build(out)) {
  # Temporarily increase blot label fonts 50%
  saved_fs <- FS; saved_hh <- HEADER_H
  FS       <<- 23L
  HEADER_H <<- 57L

  lane_labels_sep <- c("Ctrl", "ProNGF\n30 min", "ProNGF\n45 min", "ProNGF\n60 min")

  soma_comp <- build_composite(
    tau_img     = image_read("ImagesTif/ELINA_2025-09-03_12h27m08s_DyLight_800_tau-soma.tif"),
    act_img     = image_read("ImagesTif/ELINA_2025-09-03_14h40m53s_DyLight_800_actin-soma.tif"),
    tau_kda="56 kDa", act_kda="42 kDa", tau_label="Tau", act_label="Actin",
    lane_labels=lane_labels_sep, title_label="Soma"
  )
  axon_comp <- build_composite(
    tau_img     = image_read("ImagesTif/ELINA_2025-09-03_12h27m08s_DyLight_800_tau-axons.tif"),
    act_img     = image_read("ImagesTif/ELINA_2025-09-03_14h40m53s_DyLight_800_actin-axons.tif"),
    tau_kda="56 kDa", act_kda="42 kDa", tau_label="Tau", act_label="Actin",
    lane_labels=lane_labels_sep, title_label="Axon"
  )

  lane_map_sep <- read_csv("ImagesCSV/LaneMapping_ExperimentSep25 - Copy.csv", show_col_types=FALSE)
  actin_sep    <- read_csv("ImagesCSV/Sep03_DyLight800_actin.csv", show_col_types=FALSE) |>
    rename(Lane=1, Actin=Area)
  tau_sep      <- read_csv("ImagesCSV/Sep03_DyLight800_tau.csv",   show_col_types=FALSE) |>
    rename(Lane=1, Tau=Area)

  # Restore globals
  FS <<- saved_fs; HEADER_H <<- saved_hh

  df_sep <- lane_map_sep |>
    left_join(tau_sep,   by="Lane") |>
    left_join(actin_sep, by="Lane") |>
    mutate(Tau_Actin   = Tau / Actin,
           Condition   = factor(Condition, levels=c("Ctrl","ProNGF 30min","ProNGF 45min","ProNGF 60min")),
           Compartment = factor(Compartment, levels=c("Soma","Axon")))

  pA <- ggdraw() + draw_image(soma_comp)
  pB <- ggdraw() + draw_image(axon_comp)
  pC <- ggplot(df_sep, aes(Condition, Tau_Actin, fill=Compartment)) +
    geom_col(position=position_dodge(width=0.65), width=0.6, color="white") +
    scale_fill_manual(values=PAL_COMP) +
    scale_y_continuous(expand=expansion(mult=c(0,0.12))) +
    labs(x=NULL, y="Tau / Actin (a.u.)", fill="Compartment") +
    theme_wb() +
    theme(legend.position="right",
          axis.text.x = element_text(angle = 35, hjust = 1, size = 22))

  fig <- plot_grid(
    plot_grid(pA, pB, ncol=2, labels=c("A","B"), label_size=18, label_fontface="bold"),
    pC,
    nrow=2, labels=c("","C"), label_size=18, label_fontface="bold",
    rel_heights=c(1, 0.8)
  )
  save_fig(out, fig, width=14, height=10)
} else { message("Cached: ", out) }
```

---

## Western Blot — February 2026, 1st (APP Knockdown)

```{r build-feb1-combined}
out <- "figures/precomputed/fig-feb1-combined.png"

if (needs_build(out)) {
  # ── Wider blot with all 12 lane labels, bigger fonts ────────────────────
  saved_pw <- PANEL_W; saved_tw <- TOTAL_W; saved_fs <- FS; saved_hh <- HEADER_H
  PANEL_W  <<- 1000L
  TOTAL_W  <<- LEFT_W + PANEL_W + RIGHT_W
  FS       <<- 23L     # 50% bigger than default 15
  HEADER_H <<- 57L     # taller for bigger font

  # Order: Axon first (lanes 1-6), then Soma (lanes 7-12)
  lane_labels_feb1 <- c("Ctrl","ProNGF\n45 min","ProNGF\n60 min",
                         "ProNGF\n75 min","siAPP","siAPP +\nproNGF",
                         "Ctrl","ProNGF\n45 min","ProNGF\n60 min",
                         "ProNGF\n75 min","siAPP","siAPP +\nproNGF")

  tau_img <- fit_w(image_read("ImagesTif/ELINA_2026-02-12_13h04m41s_IRDye_680RD_crop_invert-1.tif")) |> add_border()
  act_img <- fit_w(image_read("ImagesTif/ELINA_2026-02-05_12h18m48s_IRDye_800CW_crop_invert-1.tif")) |> add_border()
  gap     <- image_blank(TOTAL_W, GAP_H, color = BG)

  # Title row: "Axon" centered over first half, "Soma" over second half
  half_w    <- as.integer(PANEL_W / 2L)
  title_fs  <- FS + 22L
  title_row <- image_blank(TOTAL_W, 70L, color = BG) |>
    image_annotate("Axon", size = title_fs, color = "black", font = "sans",
                   weight = 700, gravity = "NorthWest",
                   location = paste0("+", LEFT_W + half_w %/% 2L - 22L, "+8")) |>
    image_annotate("Soma", size = title_fs, color = "black", font = "sans",
                   weight = 700, gravity = "NorthWest",
                   location = paste0("+", LEFT_W + half_w + half_w %/% 2L - 22L, "+8"))

  header <- make_header(lane_labels_feb1)

  feb1_comp <- image_append(
    c(title_row, header,
      make_wb_row(tau_img, "65 kDa\n56 kDa", "panTau"), gap,
      make_wb_row(act_img, "42 kDa", "Actin")),
    stack = TRUE
  ) |> image_border(BG, "8x8")

  # Restore globals
  PANEL_W <<- saved_pw; TOTAL_W <<- saved_tw; FS <<- saved_fs; HEADER_H <<- saved_hh

  # ── Quantification from remeasured soma+axon CSVs ───────────────────────
  all_cond <- c("Ctrl","ProNGF 45min","ProNGF 60min",
                "ProNGF 75min","siAPP","siAPP + proNGF")

  tau_all <- read_csv("ImagesCSV/Feb05_IRDye_680_panTau_quantification_soma_and_axons.csv",
                      show_col_types=FALSE) |>
    rename(lane=1, tau=Area)
  act_all <- read_csv("ImagesCSV/Feb05_IRDye_800_Ms_Act_quantification_soma_and_axon.csv",
                      show_col_types=FALSE) |>
    rename(lane=1, actin=Area)

  # Lanes 1-6 = Axon, 7-12 = Soma
  df_feb1 <- inner_join(tau_all, act_all, by="lane") |>
    mutate(Condition   = factor(rep(all_cond, 2), levels=all_cond),
           Compartment = factor(rep(c("Axon","Soma"), each=6),
                                levels=c("Soma","Axon")),
           ratio       = tau / actin)

  # ── Panels: A = blot, B = panTau/Actin ratio ───────────────────────────
  pA <- ggdraw() + draw_image(feb1_comp)

  pB <- ggplot(df_feb1, aes(Condition, ratio, fill=Compartment)) +
    geom_col(position=position_dodge(width=0.65), width=0.6, color="white") +
    scale_fill_manual(values=PAL_COMP) +
    scale_y_continuous(expand=expansion(mult=c(0,0.12))) +
    labs(x=NULL, y="panTau / Actin (a.u.)", fill="Compartment") +
    theme_wb() +
    theme(legend.position="right",
          axis.text.x = element_text(angle = 35, hjust = 1, size = 22))

  fig <- plot_grid(pA, pB, nrow=2,
                   labels=c("A","B"), label_size=18, label_fontface="bold",
                   rel_heights=c(1, 0.8))
  save_fig(out, fig, width=14, height=12)
} else { message("Cached: ", out) }
```

---

## Western Blot — February 2026, 2nd (Phospho-Tau)

```{r build-feb2-combined}
out <- "figures/precomputed/fig-feb2-combined.png"

if (needs_build(out)) {
  lane_map_2 <- read_csv("ImagesCSV/LaneMapping_ExperimentJan26_2ndWB.csv",
                          show_col_types=FALSE) |>
    mutate(Lane=as.integer(Lane), Condition=factor(Condition, levels=unique(Condition)))
  condition_levels_2 <- levels(lane_map_2$Condition)

  feb2_comp <- build_composite(
    tau_img     = image_read("ImagesTif/ELINA_2026-02-13_12h41m46s_IRDye_680RD_-tau.tif"),
    act_img     = image_read("ImagesTif/ELINA_2026-02-13_12h40m54s_IRDye_800CW_-actin.tif"),
    tau_kda="56 kDa", act_kda="42 kDa", tau_label="pTau", act_label="Actin",
    lane_labels=condition_levels_2, title_label="Soma"
  )

  band_map_2     <- read_csv("ImagesCSV/BandMapping_ExperimentJan26_2ndWB - Copy.csv", show_col_types=FALSE)
  band_map_680_2 <- band_map_2 |> filter(Channel==680)
  band_map_800_2 <- band_map_2 |> filter(Channel==800)

  data_680_2 <- read_csv("ImagesCSV/Feb26_IRDye_680RD_Ms_panTau_actin_quantification.csv",
                          show_col_types=FALSE) |>
    rename(area=Area) |>
    left_join(band_map_680_2, by=c("band"="Band")) |>
    left_join(lane_map_2,    by=c("lane"="Lane")) |>
    mutate(Condition=factor(Condition, levels=condition_levels_2))

  data_800_2 <- read_csv("ImagesCSV/Feb26_IRDye_800_Rb_pTau_p622_p202_quantification.csv",
                          show_col_types=FALSE) |>
    rename(area=Area) |>
    left_join(band_map_800_2, by=c("band"="Band")) |>
    left_join(lane_map_2,    by=c("lane"="Lane")) |>
    mutate(Condition=factor(Condition, levels=condition_levels_2))

  wide_800_2 <- data_800_2 |>
    select(lane, Condition, Protein, area) |>
    pivot_wider(names_from=Protein, values_from=area) |>
    mutate(Tau_Actin=pTau56/Actin)

  ratio_sum_2 <- data_680_2 |>
    group_by(lane, Condition) |>
    summarise(tau_total=sum(area, na.rm=TRUE), .groups="drop") |>
    left_join(data_800_2 |> filter(Protein=="Actin") |> select(lane, actin=area), by="lane") |>
    mutate(ratio=tau_total/actin, Condition=factor(Condition, levels=condition_levels_2))

  pA <- ggdraw() + draw_image(feb2_comp)
  p_pt <- ggplot(wide_800_2, aes(Condition, Tau_Actin)) +
    geom_col(fill=PAL_COMP["Soma"], colour="black", width=0.65) +
    labs(title="pTau56 / Actin (800 nm)", x=NULL, y="pTau56 / Actin (a.u.)") + theme_wb()
  p_tt <- ggplot(ratio_sum_2, aes(Condition, ratio)) +
    geom_col(fill=PAL_COMP["Soma"], colour="black", width=0.65) +
    labs(title="Total Tau (680 nm) / Actin", subtitle="(pTau65 + pTau56) / Actin",
         x=NULL, y="Total Tau / Actin (a.u.)") + theme_wb()
  pB <- plot_grid(p_pt, p_tt, ncol=2)

  fig <- plot_grid(pA, pB, ncol=2,
                   labels=c("A","B"), label_size=18, label_fontface="bold")
  save_fig(out, fig, width=14, height=7)
} else { message("Cached: ", out) }
```

---

## ProNGF crops — 2×2 panel (ImageJ-exported TIFs)

```{r build-pronGF-crops-panel}
out <- "figures/precomputed/fig-pronGF-crops-panel.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_072525_20260318_042930"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ <-   80L

  # PNGs exported from ImageJ — colors and contrast already set
  tiles <- list(
    list(file  = file.path(DIR, "C4-ProNGF_Axons_p75_488_Tuj1_555__Tau_633_n1-1_croped-1_FINAL.png"),
         label = "Tau", col = "white"),
    list(file  = file.path(DIR, "C2-ProNGF_Axons_p75_488_Tuj1_555__Tau_633_n1-1_croped_FINAL.png"),
         label = "p75", col = "green"),
    list(file  = file.path(DIR, "C1-ProNGF_Axons_p75_488_Tuj1_555__Tau_633_n1-1_croped-1_FINAL.png"),
         label = "Tuj1", col = "red"),
    list(file  = file.path(DIR, "ProNGF_Axons_p75_488_Tuj1_555__Tau_633_n1-1_croped_composite-1_FINAL.png"),
         label = "Composite", col = "white")
  )

  add_label <- function(img, label, col) {
    image_annotate(img, label,
                   gravity  = "SouthWest",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  }

  imgs <- lapply(tiles, function(t) {
    img <- image_read(t$file)
    img <- image_scale(img, paste0(IMG_W, "x"))
    add_label(img, t$label, t$col)
  })

  h     <- image_info(imgs[[1]])$height
  gap_v <- image_blank(GAP,               h,   color = "white")
  gap_h <- image_blank(IMG_W * 2L + GAP, GAP,  color = "white")

  row1     <- image_append(c(imgs[[1]], gap_v, imgs[[2]]))
  row2     <- image_append(c(imgs[[3]], gap_v, imgs[[4]]))
  combined <- image_append(c(row1, gap_h, row2), stack = TRUE)

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Ctrl crops — 2×2 panel (ImageJ-exported PNGs)

```{r build-ctrl-crops-panel}
out <- "figures/precomputed/fig-ctrl-crops-panel.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_072525_20260318_042930"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ <-   80L

  tiles <- list(
    list(file  = file.path(DIR, "C4-Ctrl_Axons_p75_488_Tuj1_555__Tau_633_n1-2_FINAL.png"),
         label = "Tau", col = "white"),
    list(file  = file.path(DIR, "C2-Ctrl_Axons_p75_488_Tuj1_555__Tau_633_n1-croped-1_FINAL.png"),
         label = "p75", col = "green"),
    list(file  = file.path(DIR, "C1-Ctrl_Axons_p75_488_Tuj1_555__Tau_633_n1-1_croped-1_FINAL.png"),
         label = "Tuj1", col = "red"),
    list(file  = file.path(DIR, "Ctrl_Axons_p75_488_Tuj1_555__Tau_633_n1-1_composite-1_FINAL.png"),
         label = "Composite", col = "white")
  )

  add_label <- function(img, label, col) {
    image_annotate(img, label,
                   gravity  = "SouthWest",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  }

  imgs <- lapply(tiles, function(t) {
    img <- image_read(t$file)
    img <- image_scale(img, paste0(IMG_W, "x"))
    add_label(img, t$label, t$col)
  })

  h     <- image_info(imgs[[1]])$height
  gap_v <- image_blank(GAP,               h,   color = "white")
  gap_h <- image_blank(IMG_W * 2L + GAP, GAP,  color = "white")

  row1     <- image_append(c(imgs[[1]], gap_v, imgs[[2]]))
  row2     <- image_append(c(imgs[[3]], gap_v, imgs[[4]]))
  combined <- image_append(c(row1, gap_h, row2), stack = TRUE)

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Ctrl TrkB / Tau — 2×2 panel (ImageJ-exported PNGs)

```{r build-trkb-tau-panel}
out <- "figures/precomputed/fig-trkb-tau-panel.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_070825_20260317_130135"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ <-   80L

  # Row 1: Ctrl — TrkB | Tau | Composite
  # Row 2: ProNGF — TrkB | Tau | Composite
  tiles <- list(
    list(file  = file.path(DIR, "C2-Ctrl_Axons_TrkB_488_TAU_555_n1-1_croped-1_FINAL.png"),
         label = "Ctrl — TrkB", col = "green"),
    list(file  = file.path(DIR, "C1-Ctrl_Axons_TrkB_488_TAU_555_n1-1_FINAL-1.png"),
         label = "Ctrl — Tau", col = "red"),
    list(file  = file.path(DIR, "Ctrl_Axons_TrkB_488_TAU_555_n1-1_FINAL_merged-1.png"),
         label = "Ctrl — Composite", col = "white"),
    list(file  = file.path(DIR, "C2-ProNGF_Axons_TrkB_488_TAU_555_n2-green_trkB.png"),
         label = "ProNGF — TrkB", col = "green"),
    list(file  = file.path(DIR, "C1-ProNGF_Axons_TrkB_488_TAU_555_n2-1_red_tau.png"),
         label = "ProNGF — Tau", col = "red"),
    list(file  = file.path(DIR, "ProNGF_Axons_TrkB_488_TAU_555_n2-1_croped-composite-1.png"),
         label = "ProNGF — Composite", col = "white")
  )

  add_label <- function(img, label, col) {
    image_annotate(img, label,
                   gravity  = "SouthWest",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  }

  imgs <- lapply(tiles, function(t) {
    img <- image_read(t$file)
    img <- image_scale(img, paste0(IMG_W, "x"))
    add_label(img, t$label, t$col)
  })

  h     <- image_info(imgs[[1]])$height
  gap_v <- image_blank(GAP,                    h,   color = "white")
  gap_h <- image_blank(IMG_W * 3L + GAP * 2L, GAP,  color = "white")

  row1 <- image_append(c(imgs[[1]], gap_v, imgs[[2]], gap_v, imgs[[3]]))
  row2 <- image_append(c(imgs[[4]], gap_v, imgs[[5]], gap_v, imgs[[6]]))
  combined <- image_append(c(row1, gap_h, row2), stack = TRUE)

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Tuj1 / Tau sequential — Ctrl vs ProNGF (MF_090825, ImageJ PNGs)

```{r build-tuj1-tau-sequential-panel}
out <- "figures/precomputed/fig-tuj1-tau-sequential-panel.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_090825_20260309_134939"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ <-   80L

  # Single row: Ctrl Tuj1 | Ctrl Tau | Ctrl Comp | ProNGF Tuj1 | ProNGF Tau | ProNGF Comp
  tiles <- list(
    list(file  = file.path(DIR, "C2-Ctrl-Tuj1_488-Tau_555_2-3.png"),
         label = "Ctrl — Tuj1", col = "green"),
    list(file  = file.path(DIR, "C1-Ctrl-Tuj1_488-Tau_555_2-3.png"),
         label = "Ctrl — Tau", col = "red"),
    list(file  = file.path(DIR, "Ctrl-Tuj1_488-Tau_555_2-1-3.png"),
         label = "Ctrl — Composite", col = "white"),
    list(file  = file.path(DIR, "C2-ProNGF_in_Axons_Tuj1_488_Tau_555_1-1_croped-1.png"),
         label = "ProNGF — Tuj1", col = "green"),
    list(file  = file.path(DIR, "C1-ProNGF_in_Axons_Tuj1_488_Tau_555_1-1_croped-1.png"),
         label = "ProNGF — Tau", col = "red"),
    list(file  = file.path(DIR, "ProNGF_in_Axons_Tuj1_488_Tau_555_1-1_croped-1.png"),
         label = "ProNGF — Composite", col = "white")
  )

  add_label <- function(img, label, col) {
    image_annotate(img, label,
                   gravity  = "SouthEast",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  }

  imgs <- lapply(tiles, function(t) {
    img <- image_read(t$file)
    img <- image_scale(img, paste0(IMG_W, "x"))
    add_label(img, t$label, t$col)
  })

  h     <- image_info(imgs[[1]])$height
  gap_v <- image_blank(GAP, h, color = "white")

  combined <- image_append(c(imgs[[1]], gap_v, imgs[[2]], gap_v, imgs[[3]],
                             gap_v, imgs[[4]], gap_v, imgs[[5]], gap_v, imgs[[6]]))

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Western Blot — Feb 2026 2nd: pTau + Total Tau + Actin (3-row composite)

```{r build-feb2-3row}
out <- "figures/precomputed/fig-feb2-ptau-totaltau-actin.png"

if (needs_build(out)) {
  saved_pw <- PANEL_W; saved_tw <- TOTAL_W; saved_fs <- FS; saved_hh <- HEADER_H; saved_rw <- RIGHT_W
  PANEL_W  <<- 800L
  RIGHT_W  <<- 140L
  TOTAL_W  <<- LEFT_W + PANEL_W + RIGHT_W
  FS       <<- 23L
  HEADER_H <<- 57L

  lane_labels <- c("Ctrl", "ProNGF\n45 min", "ProNGF\n60 min",
                    "ProNGF\n75 min", "siAPP", "siAPP +\nproNGF")

  ptau_img <- fit_w(image_read("ImagesTif/ELINA_2026-02-13_12h41m46sIRDye 680RD-1_croped_inverted_pTau181.tif")) |> add_border()
  ttau_img <- fit_w(image_read("ImagesTif/ELINA_2026-02-13_12h40m54sIRDye 800CW-1_crop_invert_totalTau.tif"))   |> add_border()
  act_img  <- fit_w(image_read("ImagesTif/ELINA_2026-02-13_12h40m54s_IRDye 800CW_1_actin.tif"))                 |> add_border()

  gap <- image_blank(TOTAL_W, GAP_H, color = BG)

  title_row <- image_blank(TOTAL_W, 70L, color = BG) |>
    image_annotate("Soma", size = FS + 22, color = "black", font = "sans",
                   weight = 700, gravity = "North", location = "+0+6")

  header <- make_header(lane_labels)

  feb2_3row <- image_append(
    c(title_row, header,
      make_wb_row(ptau_img, "65 kDa\n56 kDa", "pTau181"), gap,
      make_wb_row(ttau_img, "56 kDa",          "panTau"),  gap,
      make_wb_row(act_img,  "42 kDa",          "Actin")),
    stack = TRUE
  ) |> image_border(BG, "8x8")

  image_write(feb2_3row, out, format = "png")

  # Restore globals
  PANEL_W <<- saved_pw; RIGHT_W <<- saved_rw; TOTAL_W <<- saved_tw; FS <<- saved_fs; HEADER_H <<- saved_hh
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## TrkB / Tau IF Grid v2 — All 6 side-by-side (MF_070825)

```{r build-trkb-tau-v2}
out <- "figures/precomputed/fig-trkb-tau-v3.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_070825_20260317_130135"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ <-  100L
  HDR_FONT <-  150L  # treatment header font
  HDR_H   <-  180L   # treatment header row height

  # Same 6 images as fig-trkb-tau-2x3: Ctrl (TrkB, Tau, Composite), ProNGF (TrkB, Tau, Composite)
  tiles <- list(
    list(file = "ctrl_trkB_green.png",               label = "TrkB",      col = "green"),
    list(file = "ctrl_tau_red.png",                   label = "Tau",       col = "red"),
    list(file = "Ctrl_Axons_TrkB_tau_composite_2.png",  label = "Composite", col = "white"),
    list(file = "proNGF_trkB_green.png",              label = "TrkB",      col = "green"),
    list(file = "proNGF_tau_red.png",                 label = "Tau",       col = "red"),
    list(file = "ProNGF_Axons_TrkB_tau_composite.png",label = "Composite", col = "white")
  )

  # Read, scale, add channel label on image
  imgs <- lapply(tiles, function(t) {
    img <- image_read(file.path(DIR, t$file)) |>
      image_scale(paste0(IMG_W, "x"))
    image_annotate(img, t$label,
                   gravity  = "SouthWest",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = t$col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  })

  h     <- image_info(imgs[[1]])$height
  gap_v <- image_blank(GAP, h, color = "white")

  # Single row: all 6 images side by side
  img_row <- image_append(c(imgs[[1]], gap_v, imgs[[2]], gap_v, imgs[[3]],
                            gap_v,
                            imgs[[4]], gap_v, imgs[[5]], gap_v, imgs[[6]]))

  row_w       <- image_info(img_row)$width
  ctrl_w      <- image_info(imgs[[1]])$width * 3L + GAP * 2L
  prongf_w    <- image_info(imgs[[4]])$width * 3L + GAP * 2L

  # Treatment headers centered over each group of 3
  header <- image_blank(row_w, HDR_H, color = "white")
  ctrl_center   <- as.integer(ctrl_w / 2L)
  prongf_center <- ctrl_w + GAP + as.integer(prongf_w / 2L)

  header <- header |>
    image_annotate("Ctrl", gravity = "North",
                   location = paste0("+", ctrl_center - as.integer(row_w / 2L), "+10"),
                   size = HDR_FONT, color = "black", font = "Arial-Bold") |>
    image_annotate("ProNGF", gravity = "North",
                   location = paste0("+", prongf_center - as.integer(row_w / 2L), "+10"),
                   size = HDR_FONT, color = "black", font = "Arial-Bold")

  combined <- image_append(c(header, img_row), stack = TRUE)

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Tuj1 / Tau sequential v2 — side-by-side with treatment headers (MF_090825)

```{r build-tuj1-tau-sequential-panel-v2}
out <- "figures/precomputed/fig-tuj1-tau-sequential-panel-v2.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_090825_20260309_134939"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ  <-   80L
  HDR_FONT <-  150L   # treatment header font
  HDR_H    <-  180L   # header row height for treatment labels

  # Ctrl tiles
  ctrl_tiles <- list(
    list(file  = file.path(DIR, "C2-Ctrl-Tuj1_488-Tau_555_2-3.png"),
         label = "Tuj1", col = "green"),
    list(file  = file.path(DIR, "C1-Ctrl-Tuj1_488-Tau_555_2-3.png"),
         label = "Tau", col = "red"),
    list(file  = file.path(DIR, "Ctrl-Tuj1_488-Tau_555_2-1-3.png"),
         label = "Composite", col = "white")
  )

  # ProNGF tiles
  prongf_tiles <- list(
    list(file  = file.path(DIR, "C2-ProNGF_in_Axons_Tuj1_488_Tau_555_1-1_croped-1.png"),
         label = "Tuj1", col = "green"),
    list(file  = file.path(DIR, "C1-ProNGF_in_Axons_Tuj1_488_Tau_555_1-1_croped-1.png"),
         label = "Tau", col = "red"),
    list(file  = file.path(DIR, "ProNGF_in_Axons_Tuj1_488_Tau_555_1-1_croped-1.png"),
         label = "Composite", col = "white")
  )

  add_label <- function(img, label, col) {
    image_annotate(img, label,
                   gravity  = "SouthEast",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  }

  read_and_label <- function(tiles) {
    lapply(tiles, function(t) {
      img <- image_read(t$file) |> image_scale(paste0(IMG_W, "x"))
      add_label(img, t$label, t$col)
    })
  }

  ctrl_imgs   <- read_and_label(ctrl_tiles)
  prongf_imgs <- read_and_label(prongf_tiles)

  h     <- image_info(ctrl_imgs[[1]])$height
  gap_v <- image_blank(GAP, h, color = "white")

  # All 6 images in one row: Ctrl (Tuj1|Tau|Comp) | gap | ProNGF (Tuj1|Tau|Comp)
  img_row <- image_append(c(ctrl_imgs[[1]], gap_v, ctrl_imgs[[2]], gap_v, ctrl_imgs[[3]],
                            gap_v,
                            prongf_imgs[[1]], gap_v, prongf_imgs[[2]], gap_v, prongf_imgs[[3]]))

  row_w      <- image_info(img_row)$width
  group_w    <- image_info(ctrl_imgs[[1]])$width * 3L + GAP * 2L

  # Treatment headers centered over each group of 3
  ctrl_center   <- as.integer(group_w / 2L)
  prongf_center <- group_w + GAP + as.integer(group_w / 2L)

  header <- image_blank(row_w, HDR_H, color = "white") |>
    image_annotate("Ctrl", gravity = "North",
                   location = paste0("+", ctrl_center - as.integer(row_w / 2L), "+10"),
                   size = HDR_FONT, color = "black", font = "Arial-Bold") |>
    image_annotate("ProNGF", gravity = "North",
                   location = paste0("+", prongf_center - as.integer(row_w / 2L), "+10"),
                   size = HDR_FONT, color = "black", font = "Arial-Bold")

  combined <- image_append(c(header, img_row), stack = TRUE)

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Western Blot — Feb 2026 1st (APP Knockdown) — Alt tau crop (Feb 06)

```{r build-feb1-combined-alt}
out <- "figures/precomputed/fig-feb1-combined-alt.png"

if (needs_build(out)) {
  saved_pw <- PANEL_W; saved_tw <- TOTAL_W; saved_fs <- FS; saved_hh <- HEADER_H
  PANEL_W  <<- 1000L
  TOTAL_W  <<- LEFT_W + PANEL_W + RIGHT_W
  FS       <<- 23L
  HEADER_H <<- 57L

  lane_labels_feb1 <- c("Ctrl","ProNGF\n45 min","ProNGF\n60 min",
                         "ProNGF\n75 min","siAPP","siAPP +\nproNGF",
                         "Ctrl","ProNGF\n45 min","ProNGF\n60 min",
                         "ProNGF\n75 min","siAPP","siAPP +\nproNGF")

  tau_img <- fit_w(image_read("ImagesTif/ELINA_2026-02-12_13h04m41s_IRDye_680RD_crop_invert-1.tif")) |> add_border()
  act_img <- fit_w(image_read("ImagesTif/ELINA_2026-02-05_12h18m48s_IRDye_800CW_crop_invert-1.tif")) |> add_border()
  gap     <- image_blank(TOTAL_W, GAP_H, color = BG)

  half_w    <- as.integer(PANEL_W / 2L)
  title_fs  <- FS + 22L
  title_row <- image_blank(TOTAL_W, 70L, color = BG) |>
    image_annotate("Axon", size = title_fs, color = "black", font = "sans",
                   weight = 700, gravity = "NorthWest",
                   location = paste0("+", LEFT_W + half_w %/% 2L - 22L, "+8")) |>
    image_annotate("Soma", size = title_fs, color = "black", font = "sans",
                   weight = 700, gravity = "NorthWest",
                   location = paste0("+", LEFT_W + half_w + half_w %/% 2L - 22L, "+8"))

  header <- make_header(lane_labels_feb1)

  feb1_comp_alt <- image_append(
    c(title_row, header,
      make_wb_row(tau_img, "65 kDa\n56 kDa", "panTau"), gap,
      make_wb_row(act_img, "42 kDa", "Actin")),
    stack = TRUE
  ) |> image_border(BG, "8x8")

  # Reuse same quantification as fig-feb1-combined
  all_cond <- c("Ctrl","ProNGF 45min","ProNGF 60min",
                "ProNGF 75min","siAPP","siAPP + proNGF")

  tau_all <- read_csv("ImagesCSV/Feb05_IRDye_680_panTau_quantification_soma_and_axons.csv",
                      show_col_types=FALSE) |>
    rename(lane=1, tau=Area)
  act_all <- read_csv("ImagesCSV/Feb05_IRDye_800_Ms_Act_quantification_soma_and_axon.csv",
                      show_col_types=FALSE) |>
    rename(lane=1, actin=Area)

  df_feb1 <- inner_join(tau_all, act_all, by="lane") |>
    mutate(Condition   = factor(rep(all_cond, 2), levels=all_cond),
           Compartment = factor(rep(c("Axon","Soma"), each=6),
                                levels=c("Soma","Axon")),
           ratio       = tau / actin)

  pA <- ggdraw() + draw_image(feb1_comp_alt)

  pB <- ggplot(df_feb1, aes(Condition, ratio, fill=Compartment)) +
    geom_col(position=position_dodge(width=0.65), width=0.6, color="white") +
    scale_fill_manual(values=PAL_COMP) +
    scale_y_continuous(expand=expansion(mult=c(0,0.12))) +
    labs(x=NULL, y="panTau / Actin (a.u.)", fill="Compartment") +
    theme_wb() +
    theme(legend.position="right",
          axis.text.x = element_text(angle = 35, hjust = 1, size = 22))

  fig <- plot_grid(pA, pB, nrow=2,
                   labels=c("A","B"), label_size=18, label_fontface="bold",
                   rel_heights=c(1, 0.8))
  save_fig(out, fig, width=14, height=12)

  PANEL_W <<- saved_pw; TOTAL_W <<- saved_tw; FS <<- saved_fs; HEADER_H <<- saved_hh
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

## Quantification — Feb 2026 2nd WB: pTau56/Actin, pTau65/Actin, Tau56/Actin

```{r build-feb2-3ratio-graph}
out <- "figures/precomputed/fig-feb2-3ratio-graph.png"

if (needs_build(out)) {
  lane_map <- read_csv("ImagesCSV/LaneMapping_ExperimentJan26_2ndWB.csv",
                        show_col_types = FALSE) |>
    mutate(Lane = as.integer(Lane))

  cond_lvls <- lane_map$Condition  # Ctrl, ProNGF 45min, ... siAPP + proNGF

  # ── pTau (pSer202/pThr205): Band 1 = pTau65, Band 2 = pTau56 ──────────
  ptau <- read_csv("ImagesCSV/Feb26_p202_quantification_v2.csv",
                    show_col_types = FALSE) |>
    mutate(Protein = ifelse(Band == 1, "pTau65", "pTau56")) |>
    select(Lane, Protein, Area) |>
    pivot_wider(names_from = Protein, values_from = Area)

  # ── Total Tau + Actin (800 channel): Band 1 = Tau56, Band 2 = Actin ────
  tau_act <- read_csv("ImagesCSV/Feb26_panTau_actin_quantification_v2.csv",
                       show_col_types = FALSE) |>
    mutate(Protein = ifelse(Band == 1, "Tau56", "Actin")) |>
    select(Lane, Protein, Area) |>
    pivot_wider(names_from = Protein, values_from = Area)

  # ── Merge and compute ratios ────────────────────────────────────────────
  df <- lane_map |>
    left_join(ptau,    by = "Lane") |>
    left_join(tau_act, by = "Lane") |>
    mutate(
      pTau56_Actin = pTau56 / Actin,
      pTau65_Actin = pTau65 / Actin,
      Tau56_Actin  = Tau56  / Actin,
      Condition    = factor(Condition, levels = cond_lvls)
    )

  df_long <- df |>
    select(Condition, pTau56_Actin, pTau65_Actin, Tau56_Actin) |>
    pivot_longer(-Condition, names_to = "Ratio", values_to = "Value") |>
    mutate(Ratio = factor(Ratio,
                          levels = c("pTau65_Actin", "pTau56_Actin", "Tau56_Actin"),
                          labels = c("pTau 65 kDa / Actin",
                                     "pTau 56 kDa / Actin",
                                     "Tau 56 kDa / Actin")))

  p <- ggplot(df_long, aes(Condition, Value, fill = Ratio)) +
    geom_col(position = position_dodge(width = 0.75), width = 0.7, colour = "black") +
    scale_fill_manual(values = c("pTau 65 kDa / Actin" = "#E07B54",
                                 "pTau 56 kDa / Actin" = "#4A90D9",
                                 "Tau 56 kDa / Actin"  = "#A6A6A6")) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
    labs(x = NULL, y = "Signal / Actin (a.u.)", fill = NULL) +
    theme_wb() +
    theme(legend.position = "top",
          axis.text.x = element_text(angle = 35, hjust = 1, size = 13))

  save_fig(out, p, width = 10, height = 7)
} else { message("Cached: ", out) }
```

---

## TrkB / Tau — Ctrl vs ProNGF (new crops, 2x3 panel)

```{r build-trkb-tau-2x3}
out <- "figures/precomputed/fig-trkb-tau-2x3.png"

if (needs_build(out)) {
  DIR     <- "./ZeissImages/channels_MF_070825_20260317_130135"
  IMG_W   <- 1200L
  GAP     <-   30L
  FONT_SZ <-  100L

  # Row 1: Ctrl —  TrkB | Tau | Composite
  # Row 2: ProNGF — TrkB | Tau | Composite
  tiles <- list(
    list(file = "ctrl_trkB_green.png",              label = "TrkB",      col = "green"),
    list(file = "ctrl_tau_red.png",                 label = "Tau",       col = "red"),
    list(file = "Ctrl_Axons_TrkB_tau_composite.png",label = "Composite", col = "white"),
    list(file = "proNGF_trkB_green.png",            label = "TrkB",      col = "green"),
    list(file = "proNGF_tau_red.png",               label = "Tau",       col = "red"),
    list(file = "ProNGF_Axons_TrkB_tau_composite.png", label = "Composite", col = "white")
  )

  imgs <- lapply(tiles, function(t) {
    img <- image_read(file.path(DIR, t$file)) |>
      image_scale(paste0(IMG_W, "x"))
    image_annotate(img, t$label,
                   gravity  = "SouthWest",
                   location = "+10+8",
                   size     = FONT_SZ,
                   color    = t$col,
                   font     = "Arial-Bold",
                   boxcolor = "black")
  })

  h     <- image_info(imgs[[1]])$height
  gap_v <- image_blank(GAP,                    h,   color = "white")
  gap_h <- image_blank(IMG_W * 3L + GAP * 2L, GAP,  color = "white")

  # Row treatment labels
  LABEL_H <- 70L
  row_w   <- IMG_W * 3L + GAP * 2L
  lbl_ctrl   <- image_blank(row_w, LABEL_H, color = "white") |>
    image_annotate("Ctrl", size = FONT_SZ, color = "black",
                   font = "Arial-Bold", gravity = "West", location = "+10+0")
  lbl_pronGF <- image_blank(row_w, LABEL_H, color = "white") |>
    image_annotate("ProNGF", size = FONT_SZ, color = "black",
                   font = "Arial-Bold", gravity = "West", location = "+10+0")

  row1 <- image_append(c(imgs[[1]], gap_v, imgs[[2]], gap_v, imgs[[3]]))
  row2 <- image_append(c(imgs[[4]], gap_v, imgs[[5]], gap_v, imgs[[6]]))

  combined <- image_append(
    c(lbl_ctrl, row1, gap_h, lbl_pronGF, row2),
    stack = TRUE
  )

  image_write(combined, out, format = "png")
  message("Saved: ", out)
} else { message("Cached: ", out) }
```

---

```{r summary}
figs <- list.files("figures/precomputed", pattern="\\.png$", full.names=FALSE)
cat(sprintf("\n✓ figures/precomputed/ contains %d file(s):\n", length(figs)))
cat(paste0("  ", figs, collapse="\n"), "\n")
```
