---
title: "Western Blot Analysis - Experiment Jan 26"
author: ""
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    latex_engine: xelatex
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 4.5)
library(tidyverse)

COL_BLUE    <- "#4472C4"
COL_GREY    <- "#A6A6A6"
COL_WB1     <- "#4472C4"   # 1st WB = blue
COL_WB2_SUM <- "#2E5FA3"   # 2nd WB sum tau = dark blue
COL_WB2_PT  <- "#A6A6A6"   # 2nd WB pTau56 = grey
```

---

# First Western Blot - Axon Compartment

**Channel 680 nm:** panTau | **Channel 800 nm:** Actin
Note: Lane 1 (Ctrl) was excluded from axon analysis due to unreliable reading.

```{r wb1-axon-load}
# Conditions for axon lanes 2-6 (Ctrl/lane 1 removed)
axon_conditions <- c("ProNGF 45min", "ProNGF 60min", "ProNGF 75min",
                     "siAPP", "siAPP + proNGF")

raw_680_ax <- read_csv("ImagesTif/Feb05_IRDye_680_panTau_quantification_only_axons.csv",
                        show_col_types = FALSE) %>%
  rename(lane = 1, area = Area) %>%
  mutate(Condition = factor(axon_conditions, levels = axon_conditions),
         Protein   = "panTau")

raw_800_ax <- read_csv("ImagesTif/Feb05_IRDye_800_Ms_Act_quantification_only_axons.csv",
                        show_col_types = FALSE) %>%
  rename(lane = 1, area = Area) %>%
  mutate(Condition = factor(axon_conditions, levels = axon_conditions),
         Protein   = "Actin")
```

## Raw panTau Signal - Axon (680 nm)

```{r wb1-axon-raw-680}
ggplot(raw_680_ax, aes(x = Condition, y = area)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "1st WB Axon - Raw panTau (680 nm)",
       x = NULL, y = "Band Area (pixel units)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

## Raw Actin Signal - Axon (800 nm)

```{r wb1-axon-raw-800}
ggplot(raw_800_ax, aes(x = Condition, y = area)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "1st WB Axon - Raw Actin (800 nm)",
       x = NULL, y = "Band Area (pixel units)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

## panTau / Actin Ratio - Axon

```{r wb1-axon-ratio}
axon_ratio <- inner_join(
  raw_680_ax %>% select(lane, Condition, tau = area),
  raw_800_ax %>% select(lane, actin = area),
  by = "lane"
) %>% mutate(ratio = tau / actin)

ggplot(axon_ratio, aes(x = Condition, y = ratio)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "1st WB Axon - panTau / Actin",
       x = NULL, y = "panTau / Actin (ratio)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

---

# First Western Blot - Soma Compartment

**Channel 680 nm:** panTau | **Channel 800 nm:** Actin

```{r wb1-soma-load}
soma_conditions <- c("Ctrl", "ProNGF 45min", "ProNGF 60min",
                     "ProNGF 75min", "siAPP", "siAPP + proNGF")

raw_680_sm <- read_csv("ImagesTif/Feb05_IRDye_680_panTau_quantification_only_soma.csv",
                        show_col_types = FALSE) %>%
  rename(lane = 1, area = Area) %>%
  mutate(Condition = factor(soma_conditions, levels = soma_conditions),
         Protein   = "panTau")

raw_800_sm <- read_csv("ImagesTif/Feb05_IRDye_800_Ms_Act_quantification_only_soma.csv",
                        show_col_types = FALSE) %>%
  rename(lane = 1, area = Area) %>%
  mutate(Condition = factor(soma_conditions, levels = soma_conditions),
         Protein   = "Actin")
```

## Raw panTau Signal - Soma (680 nm)

```{r wb1-soma-raw-680}
ggplot(raw_680_sm, aes(x = Condition, y = area)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "1st WB Soma - Raw panTau (680 nm)",
       x = NULL, y = "Band Area (pixel units)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

## Raw Actin Signal - Soma (800 nm)

```{r wb1-soma-raw-800}
ggplot(raw_800_sm, aes(x = Condition, y = area)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "1st WB Soma - Raw Actin (800 nm)",
       x = NULL, y = "Band Area (pixel units)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

## panTau / Actin Ratio - Soma

```{r wb1-soma-ratio}
soma_ratio_wb1 <- inner_join(
  raw_680_sm %>% select(lane, Condition, tau = area),
  raw_800_sm %>% select(lane, actin = area),
  by = "lane"
) %>% mutate(ratio = tau / actin)

ggplot(soma_ratio_wb1, aes(x = Condition, y = ratio)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "1st WB Soma - panTau / Actin",
       x = NULL, y = "panTau / Actin (ratio)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

---

# First Western Blot - Axon vs Soma Comparison

Axon and Soma measurements side-by-side for both Tau and Actin.
Note: Ctrl is soma-only (axon lane 1 excluded).

```{r wb1-axon-soma-comparison}
tau_compare <- bind_rows(
  raw_680_ax %>% select(Condition, area) %>% mutate(Compartment = "Axon"),
  raw_680_sm %>% select(Condition, area) %>% mutate(Compartment = "Soma")
) %>% mutate(Protein = "panTau (680 nm)")

actin_compare <- bind_rows(
  raw_800_ax %>% select(Condition, area) %>% mutate(Compartment = "Axon"),
  raw_800_sm %>% select(Condition, area) %>% mutate(Compartment = "Soma")
) %>% mutate(Protein = "Actin (800 nm)")

compare_df <- bind_rows(tau_compare, actin_compare) %>%
  mutate(
    Condition   = factor(as.character(Condition), levels = soma_conditions),
    Compartment = factor(Compartment, levels = c("Axon", "Soma")),
    Protein     = factor(Protein, levels = c("panTau (680 nm)", "Actin (800 nm)"))
  )

ggplot(compare_df, aes(x = Condition, y = area, fill = Compartment)) +
  geom_col(position = position_dodge(width = 0.75), colour = "black", width = 0.65) +
  scale_fill_manual(values = c(Axon = COL_BLUE, Soma = COL_GREY)) +
  facet_wrap(~ Protein, scales = "free_y") +
  labs(title = "1st WB - Axon vs Soma",
       x = NULL, y = "Band Area (pixel units)", fill = NULL) +
  theme_classic(base_size = 12) +
  theme(axis.text.x      = element_text(angle = 35, hjust = 1),
        strip.background = element_rect(fill = "grey90"),
        legend.position  = "top")
```

---

# Second Western Blot - Soma Only

**Channel 680 nm:** pTau65 (band 1) + pTau56 (band 2) | **Channel 800 nm:** pTau56 (band 1) + Actin (band 2)

```{r wb2-load}
lane_map_2 <- read_csv("ImagesTif/LaneMapping_ExperimentJan26_2ndWB.csv",
                        show_col_types = FALSE) %>%
  mutate(Lane      = as.integer(Lane),
         Condition = factor(Condition, levels = unique(Condition)))

condition_levels_2 <- levels(lane_map_2$Condition)

band_map_2     <- read_csv("ImagesTif/BandMapping_ExperimentJan26_2ndWB.csv",
                            show_col_types = FALSE)
band_map_680_2 <- band_map_2 %>% filter(Channel == 680)
band_map_800_2 <- band_map_2 %>% filter(Channel == 800)

data_680_2 <- read_csv(
  "ImagesTif/Feb26_IRDye_680RD_Ms_panTau_actin_quantification.csv",
  show_col_types = FALSE) %>%
  rename(area = Area) %>%
  left_join(band_map_680_2, by = c("band" = "Band")) %>%
  left_join(lane_map_2,    by = c("lane" = "Lane")) %>%
  mutate(Condition = factor(Condition, levels = condition_levels_2))

data_800_2 <- read_csv(
  "ImagesTif/Feb26_IRDye_800_Rb_pTau_p622_p202_quantification.csv",
  show_col_types = FALSE) %>%
  rename(area = Area) %>%
  left_join(band_map_800_2, by = c("band" = "Band")) %>%
  left_join(lane_map_2,    by = c("lane" = "Lane")) %>%
  mutate(Condition = factor(Condition, levels = condition_levels_2))

# pTau56 / Actin from 800 nm
wide_800_2 <- data_800_2 %>%
  select(lane, Condition, Protein, area) %>%
  pivot_wider(names_from = Protein, values_from = area) %>%
  mutate(Tau_Actin = pTau56 / Actin)

# Sum of tau bands (680 nm) / Actin (800 nm)
tau_sum_2 <- data_680_2 %>%
  group_by(lane, Condition) %>%
  summarise(tau_total = sum(area, na.rm = TRUE), .groups = "drop")

actin_800_2 <- data_800_2 %>%
  filter(Protein == "Actin") %>%
  select(lane, actin = area)

ratio_sum_2 <- tau_sum_2 %>%
  left_join(actin_800_2, by = "lane") %>%
  mutate(ratio = tau_total / actin,
         Condition = factor(Condition, levels = condition_levels_2))
```

## Raw Band Measurements (2nd WB)

```{r wb2-raw}
combined_2 <- bind_rows(
  data_680_2 %>% mutate(Channel = "680 nm"),
  data_800_2 %>% mutate(Channel = "800 nm")
)

ggplot(combined_2, aes(x = Condition, y = area)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  facet_wrap(~ paste0(Channel, " | ", Protein), scales = "free_y", ncol = 2) +
  labs(title = "2nd WB Soma - Raw Band Measurements",
       x = NULL, y = "Band Area (pixel units)") +
  theme_classic(base_size = 11) +
  theme(axis.text.x      = element_text(angle = 35, hjust = 1),
        strip.background = element_rect(fill = "grey90"))
```

## pTau56 / Actin (800 nm)

```{r wb2-ratio-800}
ggplot(wide_800_2, aes(x = Condition, y = Tau_Actin)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "2nd WB Soma - pTau56 / Actin (800 nm)",
       x = NULL, y = "pTau56 / Actin (ratio)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

## Total Tau (680 nm) / Actin (800 nm)

```{r wb2-ratio-sum}
ggplot(ratio_sum_2, aes(x = Condition, y = ratio)) +
  geom_col(fill = COL_BLUE, colour = "black", width = 0.65) +
  labs(title = "2nd WB Soma - Total Tau (680 nm) / Actin (800 nm)",
       subtitle = "(pTau65 + pTau56) / Actin",
       x = NULL, y = "Total Tau / Actin (ratio)") +
  theme_classic(base_size = 12) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

## Both Tau/Actin Ratios Side-by-Side (2nd WB)

```{r wb2-combined}
wb2_combined <- bind_rows(
  ratio_sum_2  %>% select(Condition, ratio) %>% mutate(Measure = "Total Tau 680nm / Actin"),
  wide_800_2   %>% select(Condition, ratio = Tau_Actin) %>% mutate(Measure = "pTau56 800nm / Actin")
) %>% mutate(
  Condition = factor(Condition, levels = condition_levels_2),
  Measure   = factor(Measure, levels = c("Total Tau 680nm / Actin", "pTau56 800nm / Actin"))
)

ggplot(wb2_combined, aes(x = Condition, y = ratio, fill = Measure)) +
  geom_col(position = position_dodge(width = 0.75), colour = "black", width = 0.65) +
  scale_fill_manual(values = c("Total Tau 680nm / Actin" = COL_BLUE,
                               "pTau56 800nm / Actin"    = COL_GREY)) +
  labs(title = "2nd WB Soma - Tau/Actin: 680nm vs 800nm",
       x = NULL, y = "Ratio (au)", fill = NULL) +
  theme_classic(base_size = 12) +
  theme(axis.text.x    = element_text(angle = 35, hjust = 1),
        legend.position = "top")
```

---

# Cross-Experiment Comparison - Soma Only

Comparing 1st WB (panTau/Actin) vs 2nd WB (Total Tau/Actin and pTau56/Actin)
for all conditions present in both experiments.

## Actin Signal Comparison

```{r cross-actin}
actin_wb1 <- raw_800_sm %>%
  select(Condition, area) %>%
  mutate(WB = "1st WB - panTau blot")

actin_wb2 <- actin_800_2 %>%
  left_join(lane_map_2, by = c("lane" = "Lane")) %>%
  select(Condition, area = actin) %>%
  mutate(WB = "2nd WB - pTau blot",
         Condition = factor(Condition, levels = soma_conditions))

actin_both <- bind_rows(actin_wb1, actin_wb2) %>%
  mutate(Condition = factor(as.character(Condition), levels = soma_conditions),
         WB = factor(WB, levels = c("1st WB - panTau blot", "2nd WB - pTau blot")))

ggplot(actin_both, aes(x = Condition, y = area, fill = WB)) +
  geom_col(position = position_dodge(width = 0.75), colour = "black", width = 0.65) +
  scale_fill_manual(values = c("1st WB - panTau blot" = COL_WB1,
                               "2nd WB - pTau blot"   = COL_GREY)) +
  labs(title = "Soma Actin Signal - 1st vs 2nd WB",
       x = NULL, y = "Band Area (pixel units)", fill = NULL) +
  theme_classic(base_size = 12) +
  theme(axis.text.x    = element_text(angle = 35, hjust = 1),
        legend.position = "top")
```

## Tau Signal Comparison

```{r cross-tau}
tau_wb1 <- raw_680_sm %>%
  select(Condition, area) %>%
  mutate(WB = "1st WB - panTau (680nm)")

tau_wb2_sum <- tau_sum_2 %>%
  select(Condition, area = tau_total) %>%
  mutate(WB = "2nd WB - Total Tau (680nm)",
         Condition = factor(as.character(Condition), levels = soma_conditions))

tau_wb2_pt <- wide_800_2 %>%
  select(Condition, area = pTau56) %>%
  mutate(WB = "2nd WB - pTau56 (800nm)",
         Condition = factor(as.character(Condition), levels = soma_conditions))

tau_both <- bind_rows(tau_wb1, tau_wb2_sum, tau_wb2_pt) %>%
  mutate(Condition = factor(as.character(Condition), levels = soma_conditions),
         WB = factor(WB, levels = c("1st WB - panTau (680nm)",
                                    "2nd WB - Total Tau (680nm)",
                                    "2nd WB - pTau56 (800nm)")))

ggplot(tau_both, aes(x = Condition, y = area, fill = WB)) +
  geom_col(position = position_dodge(width = 0.8), colour = "black", width = 0.65) +
  scale_fill_manual(values = c("1st WB - panTau (680nm)"    = "#7EB3E8",
                               "2nd WB - Total Tau (680nm)" = COL_BLUE,
                               "2nd WB - pTau56 (800nm)"    = COL_GREY)) +
  labs(title = "Soma Tau Signal - 1st vs 2nd WB",
       x = NULL, y = "Band Area (pixel units)", fill = NULL) +
  theme_classic(base_size = 12) +
  theme(axis.text.x    = element_text(angle = 35, hjust = 1),
        legend.position = "top",
        legend.text     = element_text(size = 9))
```

## Tau / Actin Ratio Comparison

```{r cross-ratio}
ratio_wb1 <- soma_ratio_wb1 %>%
  select(Condition, ratio) %>%
  mutate(WB = "1st WB - panTau/Actin")

ratio_wb2_sum <- ratio_sum_2 %>%
  select(Condition, ratio) %>%
  mutate(WB = "2nd WB - Total Tau/Actin (680nm)",
         Condition = factor(as.character(Condition), levels = soma_conditions))

ratio_wb2_pt <- wide_800_2 %>%
  select(Condition, ratio = Tau_Actin) %>%
  mutate(WB = "2nd WB - pTau56/Actin (800nm)",
         Condition = factor(as.character(Condition), levels = soma_conditions))

ratio_both <- bind_rows(ratio_wb1, ratio_wb2_sum, ratio_wb2_pt) %>%
  mutate(Condition = factor(as.character(Condition), levels = soma_conditions),
         WB = factor(WB, levels = c("1st WB - panTau/Actin",
                                    "2nd WB - Total Tau/Actin (680nm)",
                                    "2nd WB - pTau56/Actin (800nm)")))

ggplot(ratio_both, aes(x = Condition, y = ratio, fill = WB)) +
  geom_col(position = position_dodge(width = 0.8), colour = "black", width = 0.65) +
  scale_fill_manual(values = c("1st WB - panTau/Actin"           = "#7EB3E8",
                               "2nd WB - Total Tau/Actin (680nm)" = COL_BLUE,
                               "2nd WB - pTau56/Actin (800nm)"    = COL_GREY)) +
  labs(title = "Soma Tau/Actin Ratio - 1st vs 2nd WB",
       x = NULL, y = "Tau / Actin (ratio)", fill = NULL) +
  theme_classic(base_size = 12) +
  theme(axis.text.x    = element_text(angle = 35, hjust = 1),
        legend.position = "top",
        legend.text     = element_text(size = 9))
```

---

# Session Info

```{r session-info}
sessionInfo()
```
